# fullPage <img src="http://rinterface.com/inst/images/fullPage.svg" width="200px" align="right"/>
[![Travis build status](https://travis-ci.org/RinteRface/fullPage.svg?branch=master)](https://travis-ci.org/RinteRface/fullPage) [![CRAN status](https://www.r-pkg.org/badges/version/fullPage)](https://cran.r-project.org/package=fullPage)

> Many of the amazing works of [Álvaro Trigo](https://alvarotrigo.com/) for Shiny!

```{r setup, include=FALSE}
library(htmltools)
```

```{r, echo=FALSE}
p(
  tags$a(
    href = "https://shiny.john-coene.com/fullPage",
    target = "_blank",
    class = "btn btn-default",
    "fullPage demo"
  ),
  tags$a(
    href = "https://shiny.john-coene.com/pagePiling",
    target = "_blank",
    class = "btn btn-warning",
    "pagePiling demo"
  ),
  tags$a(
    href = "https://shiny.john-coene.com/multiScroll",
    target = "_blank",
    class = "btn btn-success",
    "multiScroll demo"
  )
)
```

## Installation

Install the _stable_ version from CRAN:

```r
install.packages("fullPage")
```

Install the _dev_ version from [Github](https://github.com/RinteRface/fullPage) with:

``` r
# install.packages("remotes")
remotes::install_github("RinteRface/fullPage")
```

## Features

* [fullPage.js](https://github.com/alvarotrigo/fullPage.js/) -- functions starting with `full`.
* [pagePiling.js](https://github.com/alvarotrigo/pagePiling.js/) -- functions starting with `page`.
* [multiScroll.js](https://github.com/alvarotrigo/multiscroll.js) -- functions starting with `multi`.

All ships with:

* [Milligram](https://milligram.io/) *grid, button, typography, and themes.*

